An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
meeting edits 2

\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
  % Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H = \{H^+_{(w_1, b_1)}, \ldots, H^+_{(w_k, b_k)}\}$ such that $P = \cap \H$, and for all sets of closed halfspaces $\H'$ such that $P = \cap \H'$, we have $\H \subseteq \H'$.
  % Moreover, for each $i \in [k]$, letting $F_i := H_{(w_i, b_i)} \cap P$, the set of $\{F_1, \ldots, F_k\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
  \jessie{TODO}
\end{proof}
\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
  Add two facets and now it's a polytope.
}

@@

\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
  $x \in \reals^\Y_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
\end{claim}
\begin{proof}
  $\implies$ 
  Fix any $c \in \reals$.
  $x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
  As $y$ and $c$ were arbitrary, this shows the forward direction.

@@

\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
  $x \in \pi(F_v) \iff (x,g(x)) \in F_v \iff v \in \argmin_{v' \in \V} \inprod{v'}{x}$
\end{lemma}
\begin{proof}
  \jessie{Don't like this in align environment}
  \begin{align*}
    x \in \pi(F_v) &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
                   &\iff (x,g(x)) \in F_v \\
                   &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = \min_{v' \in \V} \inprod{v'}{x'}\} \\
                   &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
  \end{align*}
\end{proof}

@@

  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
  Take any $x\in\reals^\Y_+$.
  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, we have $(x,g(x)) \in F_v$.
  Let $c := g(x)$.
  \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}

@@

  $\implies$ 
  Fix any $x \in \reals^\Y_+$.
  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
  We know there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
  Therefore $\inprod{v'}{x} = g(x) \leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.

@@

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\end{itemize}
\begin{claim}
  $G = \cap\H$ by definition of $\risk{L}_+$.
\end{claim}
\begin{proof}

  Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
  Moreover,
  \begin{align*}
    (x,c) \in G &\iff g(x) \geq c \\
                &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V \\
                &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) \\
                &\iff \inprod{L(r)}{x} \geq c \,\, \forall r \in \R\\
                &\iff (x,c) \in H^+_{L(r)} \,\, \forall r \in \R \\
                &\iff (x,c) \in \cap \H_\V \\ 
  \end{align*}
  Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.

>>>>

\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
  % Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H = \{H^+_{(w_1, b_1)}, \ldots, H^+_{(w_k, b_k)}\}$ such that $P = \cap \H$, and for all sets of closed halfspaces $\H'$ such that $P = \cap \H'$, we have $\H \subseteq \H'$.
  % Moreover, for each $i \in [k]$, letting $F_i := H_{(w_i, b_i)} \cap P$, the set of $\{F_1, \ldots, F_k\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
  \jessie{TODO}
\end{proof}
\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
  Add two facets and now it's a polytope.
}

@@

\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
  $x \in \reals^\Y_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.

  or:
  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
\end{claim}
\begin{proof}
  $\implies$ 
  Fix any $c \in \reals$.
  $x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
  As $y$ and $c$ were arbitrary, this shows the forward direction.

@@

\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
  Let $x$, $v$.

  TFAE:

  $x \in \pi(F_v)$

  $(x,g(x)) \in F_v$

  $\inprod{v}{x}= g(x)$

  $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
\end{lemma}
\begin{proof}
  \jessie{Don't like this in align environment}
  \begin{align*}
    x \in \pi(F_v)
    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in F_v\\
    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in H_v \cap G\\
    & ...\\
    &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
    &\iff (x,g(x)) \in F_v \\
    &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = \min_{v' \in \V} \inprod{v'}{x'}\} \\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
  \end{align*}
\end{proof}

@@

  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
  Take any $x\in\reals^\Y_+$.
  Let $c := g(x)$.
  \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}

@@

  $\implies$ 
  Fix any $x \in \reals^\Y_+$.
  \raf{Need to add logic: know $G \subseteq \cap(\H_\Y \cup \cap \H_{\V'})$, so only need to show $\cap(\H_\Y \cup \cap \H_{\V'}) \subseteq G$}
  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
  \raf{Want to show $c \leq g(x)$, then done by def $G$}
  \raf{Now $(x,c) \in \cap \H_{\V'} \implies (x,c) \in H^+_{v'} \implies c \leq \inprod{v'}{x} = g(x) \implies (x,c) \in G$}

  % ...$\leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.

@@

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\end{itemize}
\begin{claim}
  $G = \cap\H$.
\end{claim}
\begin{proof}
  \raf{... by definition of $\risk{L}_+$.}

  Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
Let $x \in \reals^\Y_+$.
  \begin{align*}
    (x,c) \in G
    &\iff g(x) \geq c & \text{ explain stuff here}\\
    &\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
    &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V \\
    &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \raf{let's stick with V here}\\
    % &\iff \inprod{L(r)}{x} \geq c \,\, \forall r \in \R\\
    % &\iff (x,c) \in H^+_{L(r)} \,\, \forall r \in \R \\
    &\iff (x,c) \in \cap \H_\V \\ 
  \end{align*}
  Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.
